Formalization of Forcing in Isabelle/ZF \thanks{Supported by Secyt-UNC project 33620180100465CB and Conicet.}

### 2020-01-25 IJCAR2020/forcing_theorems.tex
digo que existen los locales

As an example of the first class, we can take a look at our
formalization of \cite[Lem.~IV.2.40(a)]{kunen2011set}. Note that the
\emph{context} of the lemma includes the assumption of \isatt{P} being
a forcing notion, and the predicate of being $M$-generic is relative
to \isatt{P}:

>>>>

As an example of the first class, we can take a look at our
formalization of \cite[Lem.~IV.2.40(a)]{kunen2011set}. Note that the
context (a ``locale'' in Isabelle terminology, namely \isatt{forcing{\isacharunderscore}data}) of the lemma 
includes the assumption of \isatt{P} being
a forcing notion, and the predicate of being $M$-generic is defined in
terms of \isatt{P}:
